---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readrdi

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/paleolimbot/readrdi/workflows/R-CMD-check/badge.svg)](https://github.com/paleolimbot/readrdi/actions)
[![Codecov test coverage](https://codecov.io/gh/paleolimbot/readrdi/branch/master/graph/badge.svg)](https://codecov.io/gh/paleolimbot/readrdi?branch=master)
<!-- badges: end -->

The goal of readrdi is to provide an non-lossy read function for acoustic doppler profiles embedded within "RDI" files generated by units manufactured by RD Instruments. The package has a focus on recovering all possible information in data.frame form, partial extraction of specific data types, and inspection of possibly corrupted files. For a function that does more interpretation and includes more tools for ADCP manipulation, use `oce::read.adp.rdi()`.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/readrdi")
```
## Example

The function you probably want is `read_rdi()`.

```{r example}
library(readrdi)
ex_file <- system.file("extdata/19101018.rdi", package = "readrdi")
rdi <- read_rdi(ex_file)
str(rdi)
```

For more detailed inspection of potentially corrupted files, you can use `rdi_index()` to locate ensembles. You can subset this index and pass it to `read_rdi()` to read a subset of the data.

```{r}
rdi_index(ex_file)
```

You can use `rdi_detect_data_types()` to look for the data types. This is mostly useful to subset and pass to `read_rdi()`.

```{r}
(types <- rdi_detect_data_types(ex_file))
str(read_rdi(ex_file, types = types["velocity"]))
```
